Simple Type Theory is not too Simple

### 2021-04-07 article.tex
Update article
Add footnotes with links

For our formalization we built upon Ballarin's work \cite{ballarin20} formalizing parts of Jacobson's \textit{Basic Algebra} textbook. We believe Ballarin's nice formalization could serve as a first stepping stone to a new algebra library for Isabelle. We also hope the present work could serve as a second stepping stone in that direction. Also, we seized the opportunity of formalizing schemes to build a new topology library despite the two existing formalizations of topology in Isabelle/HOL, namely \textit{HOL-Topological\_Spaces.thy} and \textit{HOL-Analysis/Abstract\_Topology}. Our new topology library is entirely built on modern locales without using type classes nor type declarations (via the \textit{typedef} command). In particular, our topological spaces have explicit carrier sets as part of their data instead of using \textit{UNIV} or having to define it later as the union of all the open sets. 

@@

	\bibitem{typestosets}
	Kunčar, O., Popescu, A.:
	\newblock \textit{From Types to Sets by Local Type Definition in Higher-Order Logic}. 
	\newblock J Autom Reasoning 62, 237–260 (2019)

>>>>

For our formalization we built upon Ballarin's work \cite{ballarin20} formalizing parts of Jacobson's \textit{Basic Algebra} textbook. We believe Ballarin's nice formalization could serve as a first stepping stone to a new algebra library for Isabelle. We also hope the present work could serve as a second stepping stone in that direction. Also, we seized the opportunity of formalizing schemes to build a new topology library despite the two existing formalizations of topology in Isabelle/HOL, namely \textit{HOL-Topological\_Spaces.thy}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL/Topological_Spaces.html}} and \textit{HOL-Analysis/Abstract\_Topology}\footnote{\url{https://isabelle.in.tum.de/dist/library/HOL/HOL-Analysis/Abstract_Topology.html}}. Our new topology library is entirely built on modern locales without using type classes nor type declarations (via the \textit{typedef} command). In particular, our topological spaces have explicit carrier sets as part of their data instead of using \textit{UNIV} or having to define it later as the union of all the open sets. 

@@

	\bibitem{typestosets}
	Kunčar, O., Popescu, A.:
	\newblock \textit{From Types to Sets by Local Type Definition in Higher-Order Logic}. 
	\newblock J. Autom. Reason. 62, 237–260 (2019)
